A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2023-07-13 kobakian-cook.Rmd
fixed github location
Amended development version github reference

The package can be installed from CRAN:

```{r eval=FALSE, echo = TRUE}
install.packages("sugarbag")
```

\noindent and the development version can be installed from the GitHub repository:

```{r eval=FALSE, echo = TRUE}
devtools::install_github("srkobakian","sugarbag")
```

>>>>

The package can be installed from CRAN and the development version can be installed from the GitHub repository: https://github.com/srkobakian/sugarbag.

### 2023-07-13 kobakian-cook.tex
fixed github location
Amended development version github reference

% !TeX root = RJwrapper.tex
\title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}

\author{by Stephanie Kobakian, Dianne Cook, and Earl Duncan}

@@

The package can be installed from CRAN:

\begin{verbatim}
install.packages("sugarbag")
\end{verbatim}

\noindent and the development version can be installed from the GitHub repository:

\begin{verbatim}
devtools::install_github("srkobakian","sugarbag")
\end{verbatim}

>>>>

% !TeX root = RJwrapper.tex
\title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}
\author{by Stephanie Kobakian, Dianne Cook, and Earl Duncan}

@@

The package can be installed from CRAN and the development version can be installed from the GitHub repository: \url{https://github.com/srkobakian/sugarbag}.
